\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2023-03-01 paper/si.tex
si fixes

Section~\ref{section:pairwise_comparison} gives a brief overview of the pairwise
comparison process. The pairwise comparison process consists of three phases;
(1) the mutation phase (2) the game phase and (3) the update phase. In the
update phase an individual adopts the strategy of another individual based on
their ``updating payoffs''. In the paper we explore the effect of the updating
payoffs on the evolved populations. We used as an example the prisoner's
dilemma. We focused mainly on two approaches for calculating the updating
payoffs which we referred to as the perfect memory and the limited memory
approaches. In Section~\ref{section:perfect_memory} we describe the perfect
memory approach and in Section~\ref{section:limited_memory} we present the
limited memory approach. In the limited memory approach we assume that
individuals update based on their last round payoff against one other member of
the population. The framework can easily be extended to consider more rounds,
more interactions or both. In
Sections~\ref{section:m_one_n_two}-\ref{section:m_two_n_two} we present each of
this extensions and for each a special case.
In Section~\ref{section:simulation_results} we present numerical results of the
pairwise comparison process using the several updating payoff approaches we have
presented. In Sections~\ref{section:memory_one} and~\ref{section:mutation} we
verify the main result of the paper when we no longer assume (i) that
individuals use reactive strategies but instead memory one strategies (ii) low
mutation.

% The aim of our work is to explore the effect
% of the updating payoffs on the evolution of cooperation. To this end we
% introduce a new method for calculating the updating payoffs and we compare the
% results of the new method to those of the expected payoffs. In our approach we
% do not assume that an individual has a perfect memory. Instead an individual
% remembers only a limited number of interactions and limited outcomes from each
% interaction.

@@

\begin{equation}
    \begin{blockarray}{ccc}
        & \text{cooperate} & \text{defect} \\
        \begin{block}{c(cc)}
            \text{cooperate} & b - c & -c \\
            \text{defect} & b & 0 \\
        \end{block}
    \end{blockarray}.
\end{equation}

Let \(\mathbf{u} = (b-c, -c, b, 0)\) be payoffs in a vector format, and let \(\mathcal{U}
= \{r, s, t, p\}\) denote the set of feasible payoffs, where \(r\) denotes the
payoff of mutual cooperation, \(s\) the sucker's payoff, \(t\) the temptation to
defect payoff, and \(p\) the punishment payoff.

In the following sections we present several approaches for calculating the
updating payoffs. Initially, we discuss the conventional approach of the
expected payoffs and afterwards we present our newly introduced approaches.

\section{Updating Payoffs based on the expected payoffs (perfect memory)}\label{section:perfect_memory}

The expected payoffs are the conventional payoffs used in the updating stage. We
refer to this approach as the perfect memory approach. The expected payoffs are
defined as the mean payoff of an individual in a well-mixed population that
engages in an infinitely repeated games with all other population members.
The game between two reactive strategies $s_1\!=\!(y_1, p_1, q_1$) and $s_2\!=\!(y_2,p_2,q_2)$
can be described by a Markovian process~\cite{nowak:APC:1989} with the
transition matrix \(M\),

@@

The stationary vector \(\mathbf{v}(s_1,s_2)\) is the solution to
\(\mathbf{v}(s_1,s_2) M = \mathbf{v}(s_1,s_2)\). In an infinitely repeated game
the game stage outcome for each strategy is given by,

@@

Let's assume that individuals use their expected payoffs at the updating phase.
We can calculate how easily a single defecting mutant (ALLD) can invade into a
resident population of conditional cooperators, otherwise known as generous tit
for tat (GTFT), players. Let GTFT\(= (1, 1, q)\), ALLD\(= (0, 0, 0)\), and \(k =
1\). When two GTFT players interact in an infinitely repeated game, the
stationary distribution \(\mathbf{v}(\text{GTFT}, \text{ALLD})\) 
simplifies to,

@@

This result will become important when we analyse the behaviour that emerges
from the evolutionary process. We will repeat this ``invasion analysis'' for the
rest of the updating payoffs cases.

\section{Updating Payoffs based on the Last Round Payoff of One Interaction (limited memory)}\label{section:limited_memory}

In the expected payoffs case the payoff of a pair depends on the average payoff
they received over an infinite number of turns. In the limited memory payoffs,
the payoff of a pair depends on the average payoffs they received in the last
turn. Furthermore, in expected payoffs it is assumed that a player interacts
with every member of the population, whereas in the limited memory approach a
player has one interaction. Initially, we define the probability that a reactive
strategy receives the payoff $u\!\in\! \mathcal{U}$ in the very last round of
the game against another reactive strategy
(Proposition~\ref{proposition:last_round}).

@@

\begin{equation}\label{eq:Chi}
\setlength{\arraycolsep}{1pt}
\begin{array}{llrl}
x(u_1,u_2)	 &=&\displaystyle \frac{1}{N\!-\!1}\cdot  &v_{u_1}(s_1,s_2)\cdot 1_{(u_1,u_2)\in \mathcal{U}^2_F}\\[0.5cm]
&+	
&\displaystyle \left(1\!-\!\frac{1}{N\!-\!1}\right)  
&\left[ \frac{k\!-\!1}{N\!-\!2}\frac{k\!-\!2}{N\!-\!3} v_{u_1}(s_1,s_2) v_{u_2}(s_2,s_2) + 
 \frac{k\!-\!1}{N\!-\!2}\frac{N\!-\!k\!-\!1}{N\!-\!3} v_{u_1}(s_1,s_2) v_{u_2}(s_2,s_1)\right.\\[0.5cm]
&&&\left. +\frac{N\!-\!k\!-\!1}{N\!-\!2}\frac{k\!-\!1}{N\!-\!3} v_{u_1}(s_1,s_1) v_{u_2}(s_2,s_2) + 
 \frac{N\!-\!k\!-\!1}{N\!-\!2}\frac{N\!-\!k\!-\!2}{N\!-\!3} v_{u_1}(s_1,s_1) v_{u_2}(s_2,s_1)\right].
\end{array}
\end{equation}

The first term on the right side corresponds to the case that the learner and
the role model happened to be matched during the game stage, which happens with
probability $\frac{1}{(N\!-\!1)}$. In that case, we note that only those payoff
pairs can occur that are feasible in a direct interaction,
$\splitatcommas{(u_1,u_2)\in \mathcal{U}^2_F:=\big\{ (r, r), (s, t), (t, s), (p,
p) \big\}}$, as represented by the respective indicator function. Otherwise, if
the learner and the role model did not interact directly, we need to distinguish
four different cases, depending on whether the learner was matched with a
resident or a mutant, and depending on whether the role model was matched with a
resident or a mutant.

@@

\begin{align*}
  x(r, t) = & \frac{N - 2}{N - 1} \cdot (1 - \delta + \delta q)\\
  x(r, r) = & \frac{N - 2}{N - 1} \cdot \delta (1 - q) \\
  x(s, r) = & \frac{1}{N - 1} \cdot (1 - \delta + \delta q) \\
  x(p, p) = & \frac{1}{N - 1} \cdot \delta (1 - q)
\end{align*}

@@

In the limited memory payoffs we assume that an individual recalls the last
round they received against one member of the population. This is an edge case.
The framework of the limited memory can be generalised such that an individual
considers \(m\) rounds and of \(n\) interactions. Here we discuss the case that
the update depends on the last round of \(n\) interactions.

At each step of the evolutionary process the role model and the learner now
participate in \(n\) matches. We need to define the probability that for these
matches they are paired with a mutant, with a resident or with each other. We
assume that each pair is unique, so the resident and role model can be matched
together only once at each step. A representation of the process is given in
Figure.

In the case of \(n=1\) there are five possible pairs, however, the number of
possible pairs increases non linearly as we increase the number of possible
interactions. We demonstrate this case for \(n=2\), namely, for when the role
model and the learner have two interactions.

\subsection*{Special case: Last Round Payoff of Two Interactions}

For \(n=2\) there are two stages of matching and there are twenty four possible pairs. In
the first stage the role model and the learner are matched together with a
probability $\frac{1}{N-1}$ or not with a probability $(1 - \frac{1}{N-1})$. If
they were matched together then in the second stage there are only four possible
outcomes; both of them interact with a mutant with a probability
$\frac{(k-1)(k-2)}{(N-2)(N-3)}$ and both interact with a resident with a
probability $\frac{(N-k-1)(N-k-2)}{(N-2)(N-3)}$. The last two possible pairs are
that either of them interacts with a resident whilst the other interacts with a
mutant, and this happens with a probability $\frac{(N-k-1)(k-1)}{(N-2)(N-3)}$.
In the later case, where they were not matched in the first stage, there are
four possible outcomes; both of them interact with a mutant and both interact
with a resident, either of them interacts with a resident whilst the other
interacts with a mutant. For each of the above pairs of the first stage there
are five possible pairs in the second stage; they interact with each other, both
of them interact with a mutant and both interact with a resident, either of them
interacts with a resident whilst the other interacts with a mutant.

The new possible pairs change how we define the probability that the
respective last round payoffs of two players \(s_1, s_2\) are given by \(u_1\)
and \(u_2\). The new probability denoted as \(\tilde{x}(u_1,u_2)\) is given by,

\begin{equation}
  \resizebox{.99\textwidth}{!}
  {%
$
  \setlength{\arraycolsep}{1pt}
  \begin{array}{llrl}
  \tilde{x}(u_1,u_2)	& = \displaystyle \frac{1}{N\!-\!1}\cdot v_{u_1}(s_1,s_2)\cdot 1_{(u_1,u_2)\in \mathcal{U}^2_F} \cdot A + \left(1\!-\!\frac{1}{N\!-\!1}\right) \left[ \right. \\[0.5cm] 
  & \left. v_{u_1}(s_1,s_2) _{u_2}(s_2,s_2)  \frac{\left(k - 2\right) \left(k - 1\right)}{(N\!-\!2)(N\!-\!3)}
  \left(\frac{1}{N\!-\!2}\cdot v_{u_1}(s_1,s_2)\cdot 1_{(u_1,u_2)\in \mathcal{U}^2_F} + (1 - \frac{1}{N - 2}) [B_1 + B_2 + B_3 + B_4]\right) + \right. \\[0.5cm] 
  & \left. v_{u_1}(s_1,s_2) _{u_2}(s_2,s_1)  \frac{\left(k - 1\right) \left(N - k - 1\right)}{(N\!-\!2)(N\!-\!3)} \left(\frac{1}{N\!-\!2}\cdot v_{u_1}(s_1,s_2)\cdot 1_{(u_1,u_2)\in \mathcal{U}^2_F} + (1 - \frac{1}{N - 2}) [C_1 + C_2 + C_3 + C_4]\right) + \right. \\[0.5cm] 
  & \left. v_{u_1}(s_1,s_1) _{u_2}(s_2,s_2)  \frac{\left(k - 1\right) \left(N - k - 1\right)}{(N\!-\!2)(N\!-\!3)} \left(\frac{1}{N\!-\!2}\cdot v_{u_1}(s_1,s_2)\cdot 1_{(u_1,u_2)\in \mathcal{U}^2_F} + (1 - \frac{1}{N - 2}) [D_1 + D_2 + D_3 + D_4]\right) + \right. \\[0.5cm] 
  & \left. v_{u_1}(s_1,s_1) _{u_2}(s_2,s_1)  \frac{\left(N - k - 2\right) \left(N - k - 1\right)}{(N\!-\!2)(N\!-\!3)} \left(\frac{1}{N\!-\!2}\cdot v_{u_1}(s_1,s_2)\cdot 1_{(u_1,u_2)\in \mathcal{U}^2_F} + (1 - \frac{1}{N - 2}) [E_1 + E_2 + E_3 + E_4]\right) \right]
  \end{array} $}
\end{equation}

\begin{equation}
  \resizebox{.9\textwidth}{!}
  {%
$
  \setlength{\arraycolsep}{1pt}
  \begin{array}{llrl}
  A & = \left(1\!-\!\frac{1}{N\!-\!1}\right)  \left[ \frac{k\!-\!1}{N\!-\!2}\frac{k\!-\!2}{N\!-\!3} v_{u_1}(s_1,s_2) v_{u_2}(s_2,s_2) + 
   \frac{k\!-\!1}{N\!-\!2}\frac{N\!-\!k\!-\!1}{N\!-\!3} v_{u_1}(s_1,s_2) v_{u_2}(s_2,s_1) + \right. \\[0.5cm]
   & \left. \frac{N\!-\!k\!-\!1}{N\!-\!2}\frac{k\!-\!1}{N\!-\!3} v_{u_1}(s_1,s_1) v_{u_2}(s_2,s_2) + 
   \frac{N\!-\!k\!-\!1}{N\!-\!2}\frac{N\!-\!k\!-\!2}{N\!-\!3} v_{u_1}(s_1,s_1) v_{u_2}(s_2,s_1)\right] \\[0.5cm] 
   B_1 & = \frac{\left(k - 3\right) \left(k - 2\right)}{(N - 3) (N - 4)} v_{u_1}(s_1,s_2) v_{u_2}(s_2,s_2) \quad
   B_2 = \frac{\left(k - 2\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} v_{u_1}(s_1,s_1) v_{u_2}(s_2,s_2) \\[0.5cm] 
   B_3 & = \frac{\left(k - 2\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} v_{u_1}(s_1,s_2) v_{u_2}(s_2,s_1) \quad
   B_4 = \frac{\left(N - k - 2\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} v_{u_1}(s_1,s_1) v_{u_2}(s_2,s_1) \\[0.5cm]

   C_1 & = \frac{\left(k - 3\right) \left(k - 1\right)}{(N - 3) (N - 4)} v_{u_1}(s_1,s_2) v_{u_2}(s_2,s_2) \quad
   C_2 = \frac{\left(k - 1\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} v_{u_1}(s_1,s_1) v_{u_2}(s_2,s_2) \\[0.5cm] 
   C_3 & = \frac{\left(k - 2\right) \left(N - k - 2\right)}{(N - 3) (N - 4)} v_{u_1}(s_1,s_2) v_{u_2}(s_2,s_1) \quad
   C_4 = \frac{\left(N - k - 2\right)^{2}}{(N - 3) (N - 4)} v_{u_1}(s_1,s_1) v_{u_2}(s_2,s_1) \\[0.5cm]

   D_1 & = \frac{\left(k - 2\right)^{2}}{(N - 3) (N - 4)} v_{u_1}(s_1,s_2) v_{u_2}(s_2,s_2) \quad
   D_2 = \frac{\left(k - 2\right) \left(N - k - 2\right)}{(N - 3) (N - 4)} v_{u_1}(s_1,s_1) v_{u_2}(s_2,s_2) \\[0.5cm] 
   D_3 & = \frac{\left(k - 1\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} v_{u_1}(s_1,s_2) v_{u_2}(s_2,s_1) \quad
   D_4 = \frac{\left(N - k - 3\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} v_{u_1}(s_1,s_1) v_{u_2}(s_2,s_1) \\[0.5cm]

   E_1 & = \frac{\left(k - 2\right) \left(k - 1\right)} v_{u_1}(s_1,s_2) v_{u_2}(s_2,s_2) \quad
   E_2 = \frac{\left(k - 1\right) \left(N - k - 2\right)}{(N - 3) (N - 4)} v_{u_1}(s_1,s_1) v_{u_2}(s_2,s_2) \\[0.5cm] 
   E_3 & = \frac{\left(k - 1\right) \left(N - k - 2\right)}{(N - 3) (N - 4)} v_{u_1}(s_1,s_2) v_{u_2}(s_2,s_1) \quad
   E_4 = \frac{\left(N - k - 3\right) \left(N - k - 2\right)}{(N - 3) (N - 4)} v_{u_1}(s_1,s_1) v_{u_2}(s_2,s_1) \\[0.5cm] 
  \end{array}$}
\end{equation}

The first term on the right side corresponds to the case that the learner and
the role model happened to be matched during the first stage of pairing,
followed by them being paired with another member of the population on the
second stage. The second terms corresponds to the case that the learner and the
role model interact with a mutant with a probability ($\frac{\left(k - 2\right)
\left(k - 1\right)}{(N\!-\!2)(N\!-\!3)}$). In the seconds stage, they can either
interact with each other $\frac{1}{N - 2}$ or not $(1 - \frac{1}{N - 2})$. If
they do not interact with each other, then each of the following can happen:
both of them interact with a mutant with a probability
$\frac{(k-3)(k-2)}{(N-4)(N-3)}$ and both interact with a resident with a
probability $\frac{(N-k-1)(N-k-2)}{(N-3)(N-4)}$. The last two possible pairings
are that either of them interacts with a resident whilst the other interacts
with a mutant, and this happens with a probability
$\frac{(N-k-2)(k-1)}{(N-4)(N-3)}$, and so on.

@@

In a similar fashion we can calculate the condition for which a population of
GTFT players can not be invaded by an ALLD mutant. Using the new formulation we
obtain the following probabilities \(\bar{x}(u_1, u_2)\) that the payoff of a randomly
chosen GTFT player is \(u_1\) and that the payoff of the ALLD player is \(u_2\),

>>>>

Section~\ref{section:pairwise_comparison} gives a brief overview of the pairwise
comparison process. The pairwise comparison process consists of three phases;
(1) the mutation phase (2) the game phase and (3) the update phase. In the
update phase an individual adopts the strategy of another individual based on
their ``updating payoffs''. Here we study different methods for calculating
updating payoffs and we compare their results using as an example the prisoner's
dilemma. In Section~\ref{section:perfect_memory} we describe the conventional
method used in the literature and in Section~\ref{section:limited_memory} we
present a new method which we refer to as 
limited payoff memory. In the limited payoff memory method we assume that
individuals update based on their last round payoff against one other member of
the population. The framework can easily be extended to consider more rounds,
more interactions or both. In
Sections~\ref{section:m_one_n_two}-\ref{section:m_two_n_two} we discuss each of
these extensions and for each extension we present a special case.
In Section~\ref{section:simulation_results} we present numerical results of the
pairwise comparison process using the different updating payoff methods.
In Sections~\ref{section:memory_one} and~\ref{section:mutation} we
verify the main result of this work when we no longer assume (i) that
individuals use reactive strategies but instead memory one strategies (ii) low
mutation.

@@

\begin{equation}\label{eq:donation}
    \begin{blockarray}{ccc}
        & \text{cooperate} & \text{defect} \\
        \begin{block}{c(cc)}
            \text{cooperate} & b - c & -c \\
            \text{defect} & b & 0 \\
        \end{block}
    \end{blockarray}.
\end{equation}

Let \(\mathbf{u} = (b-c, -c, b, 0)\) be Eq.~\ref{eq:donation} in a vector format, and let \(\mathcal{U}
= \{r, s, t, p\}\) denote the set of feasible payoffs, where \(r\) denotes the
payoff of mutual cooperation, \(s\) the sucker's payoff, \(t\) the temptation to
defect payoff, and \(p\) the punishment payoff.

In the following sections we present several methods for calculating the
updating payoffs. Initially, we discuss the conventional way of the
expected payoffs and afterwards we present our newly introduced methods.

\section{Updating Payoffs based on Expected Payoffs (perfect payoff memory)}\label{section:perfect_memory}

The expected payoffs are the conventional payoffs used in the updating stage.
The expected payoffs are defined as the mean payoff of an individual in a well-mixed population that
engages in an infinitely repeated games with all other population members.
The game between two reactive strategies $s_1\!=\!(y_1, p_1, q_1$) and $s_2\!=\!(y_2,p_2,q_2)$
can be described by a Markovian process~\cite{nowak:APC:1989} with the
transition matrix \(M\),

@@

The stationary vector \(\mathbf{v}(s_1,s_2)\) is the solution to
\(\mathbf{v}(s_1,s_2) M = \mathbf{v}(s_1,s_2)\). In an infinitely repeated game
the long-term average payoff of \(s_1\) and \(s_2\) are,

@@

Let's assume that individuals use their expected payoffs at the updating phase.
We can calculate how easily a single defecting mutant (ALLD) can invade into a
resident population of conditional cooperators, otherwise known as generous tit
for tat (GTFT). Let GTFT\(= (1, 1, q)\), ALLD\(= (0, 0, 0)\), and \(k =
1\). When two GTFT players interact in an infinitely repeated game, the
stationary distribution \(\mathbf{v}(\text{GTFT}, \text{ALLD})\) 
simplifies to,

@@

This result will become important when we discuss the numerical results of the
evolutionary process (Section~\ref{section:simulation_results}). We repeat this
``invasion analysis'' for the rest of the updating payoffs cases.

\section{Updating Payoffs based on the Last Round Payoff of One Interaction (limited payoff memory)}\label{section:limited_memory}

In the expected payoffs case the payoff of a pair depends on the average payoff
they received over an infinite number of turns. In the limited payoff memory,
the payoff of a pair depends on the average payoffs they received in the last
turn. Moreover, in expected payoffs it is assumed that a player interacts with
every member of the population whereas in the limited payoff memory approach a
player has one interaction.

Initially, we define the probability that a reactive strategy receives the
payoff $u\!\in\! \mathcal{U}$ in the very last round of the game against another
reactive strategy (Proposition~\ref{proposition:last_round}).

@@

\begin{equation}\label{eq:Chi}
\setlength{\arraycolsep}{1pt}
\begin{array}{llrl}
x(u_1,u_2)	 &=&\displaystyle \frac{1}{N\!-\!1}\cdot  &v_{u_1}(s_1,s_2)\cdot 1_{(u_1,u_2)\in \mathcal{U}_F}\\[0.5cm]
&+	
&\displaystyle \left(1\!-\!\frac{1}{N\!-\!1}\right)  
&\left[ \frac{k\!-\!1}{N\!-\!2}\frac{k\!-\!2}{N\!-\!3} v_{u_1}(s_1,s_2) v_{u_2}(s_2,s_2) + 
 \frac{k\!-\!1}{N\!-\!2}\frac{N\!-\!k\!-\!1}{N\!-\!3} v_{u_1}(s_1,s_2) v_{u_2}(s_2,s_1)\right.\\[0.5cm]
&&&\left. +\frac{N\!-\!k\!-\!1}{N\!-\!2}\frac{k\!-\!1}{N\!-\!3} v_{u_1}(s_1,s_1) v_{u_2}(s_2,s_2) + 
 \frac{N\!-\!k\!-\!1}{N\!-\!2}\frac{N\!-\!k\!-\!2}{N\!-\!3} v_{u_1}(s_1,s_1) v_{u_2}(s_2,s_1)\right].
\end{array}
\end{equation}

The first term on the right side corresponds to the case that the learner and
the role model happened to be matched during the game stage, which happens with
probability $\frac{1}{(N\!-\!1)}$. In that case, we note that only those payoff
pairs can occur that are feasible in a direct interaction,
$\splitatcommas{(u_1,u_2)\in \mathcal{U}_F:=\big\{ (r, r), (s, t), (t, s), (p,
p) \big\}}$, as represented by the respective indicator function. Otherwise, if
the learner and the role model did not interact directly, we need to distinguish
four different cases, depending on whether the learner was matched with a
resident or a mutant, and depending on whether the role model was matched with a
resident or a mutant.

@@

\begin{align*}
  x(r, t) = & \frac{N - 2}{N - 1} \cdot (1 - \delta + \delta q)\\
  x(r, r) = & \frac{N - 2}{N - 1} \cdot \delta (1 - q) \\
  x(s, r) = & \frac{1}{N - 1} \cdot (1 - \delta + \delta q) \\
  x(p, p) = & \frac{1}{N - 1} \cdot \delta (1 - q) \\
  x(u_1, u_2) = &  0 \text{ for all other payoff pairs } (u_1, u_2).
\end{align*}

@@

The framework of the limited memory can be generalised such that an individual
considers \(m\) rounds and of \(n\) interactions. Here we discuss the case that
the update depends on the last round of \(n\) interactions.

At each step of the evolutionary process the role model and the learner now
participate in \(n\) matches. We need to define the probability that for each of
the matches they are paired with a mutant, with a resident or with each other.
We assume that each pair is unique, so for example the resident and role model
can be matched together only once at each step. A representation of the process
is given in Figure~\ref{fig:matching_tree}. In the case of \(n=1\) there are
five possible pairs, however, the number of possible pairs increases non
linearly as we increase the number of possible interactions. We demonstrate this
case for \(n=2\), namely, for when the role model and the learner have two
interactions.

\begin{figure}[!htbp]
  \centering 
  \includegraphics[width=\textwidth]{static/matching_tree.pdf}
  \caption{\textbf{Tree diagram of the possible pairs when the learner and the role
  model have $n$ interactions.} In the diagram \((s_i, s_j)\) represent a possible
  pair. We denote the role model as $s_{RM}$ and the learner as $s_{L}$, and
  a member of the population that plays a mutant strategy is denoted as $s_{M}$ and
  a resident strategy as $s_{R}$. The role model and
  the learner need to be paired with $n$ other members of the population
  (including each other). We break down the process into stages. For the first
  pair (stage one) the role model and the mutant can be paired together (with
  probability $\frac{1}{N-1}$) or not (with probability $1 -
  \left(\frac{1}{N-1}\right)$). In the case that they are not paired together,
  both can be paired with a mutant $\frac{(k-1)(k-2)}{(N-2)(N-3)}$, with a
  resident $\frac{(N-k-1)(N-k-2)}{(N-2)(N-3)}$, or one is paired with a mutant
  whilst the other is paired with a resident $\frac{(N-k-1)(k-1)}{(N-2)(N-3)}$.
  There are five possible pairs for stage one as we have already discussed
  in Section~\ref{section:limited_memory}. In
  the second stage we need to consider if the role model and the learner
  interacted with each other. If yes, then they can not interact with each other
  again, and at each stage there are at most four possible pairs; they interact with
  mutants, with residents, or the one interacts with a mutant whilst the second
  interacts with a resident. In the case that they were not paired in stage 1
  there are five possible pairs. These pairs are the same as in stage 1,
  however now the probabilities differ. Namely, let's assume that in the
  first stage both were matched with a mutant. They interact with each
  other with a probability $\frac{1}{N-2}$ or not with a probability
  $1 - \left(\frac{1}{N-2}\right)$. In the latter case there are four
  possible pairs.
  Both can be paired with a mutant $\frac{(k-1)(k-2)}{(N-3)(N-4)}$, with a
  resident $\frac{(N-k-1)(N-k-2)}{(N-3)(N-4)}$, or one is paired with a mutant
  whilst the other is paired with a resident $\frac{(N-k-1)(k-2)}{(N-3)(N-4)}$.
  The process continues following the same logic until it reaches the $n^{\text{th}}$
  stage.}\label{fig:matching_tree}
\end{figure}

\subsection{Last Round Payoff of Two Interactions}

Here the learner and role model consider the last round payoff of two
interactions. At each time step of the evolutionary process there are twenty
four possible pairs. At the first stage there are fiver possible pairs. For four of
these pairs there are five possible pairs in the second stage (\(4 \times 5 =
20\)), and for the last one there are four possible pairs in the second stage
(20 + 4 = 24).

We assume that player \(s_1\) receives the payoff
\(u_{11}\) with their first interaction and \(u_{12}\) with their second.
Respectively, player \(s_2\) receives \(u_{21}\) and \(u_{22}\). We define the
probability that the respective last round payoffs of the two players \(s_1,
s_2\) are given by \((u_{11}, u_{11})\) and \((u_{21}, u_{22})\) as
\(x^{2}((u_{11}, u_{11}), (u_{21}, u_{22}))\) given by,

\begin{equation}
  \resizebox{.99\textwidth}{!}
  {%
$
  \setlength{\arraycolsep}{1pt}
  \begin{array}{llrl}
  x^{2}((u_{11}, u_{12}), (u_{21}, u_{22}))	& = \displaystyle \frac{1}{N\!-\!1}\cdot v_{u_{11}}(s_1,s_2)\cdot 1_{(u_{11},u_{21})\in \mathcal{U}_F} \cdot A + \left(1\!-\!\frac{1}{N\!-\!1}\right) \left[ \right. \\[0.5cm] 
  & \left. v_{u_{11}}(s_1,s_2) _{u_{21}}(s_2,s_2)  \frac{\left(k - 2\right) \left(k - 1\right)}{(N\!-\!2)(N\!-\!3)}
  \left(\frac{1}{N\!-\!2}\cdot v_{u_{11}}(s_1,s_2)\cdot 1_{(u_{11},u_{21})\in \mathcal{U}_F} + (1 - \frac{1}{N - 2}) [B_1 + B_2 + B_3 + B_4]\right) + \right. \\[0.5cm] 
  & \left. v_{u_{11}}(s_1,s_2) _{u_{21}}(s_2,s_1)  \frac{\left(k - 1\right) \left(N - k - 1\right)}{(N\!-\!2)(N\!-\!3)} \left(\frac{1}{N\!-\!2}\cdot v_{u_{11}}(s_1,s_2)\cdot 1_{(u_{11},u_{21})\in \mathcal{U}_F} + (1 - \frac{1}{N - 2}) [C_1 + C_2 + C_3 + C_4]\right) + \right. \\[0.5cm] 
  & \left. v_{u_{11}}(s_1,s_1) _{u_{21}}(s_2,s_2)  \frac{\left(k - 1\right) \left(N - k - 1\right)}{(N\!-\!2)(N\!-\!3)} \left(\frac{1}{N\!-\!2}\cdot v_{u_{11}}(s_1,s_2)\cdot 1_{(u_{11},u_{21})\in \mathcal{U}_F} + (1 - \frac{1}{N - 2}) [D_1 + D_2 + D_3 + D_4]\right) + \right. \\[0.5cm] 
  & \left. v_{u_{11}}(s_1,s_1) _{u_{21}}(s_2,s_1)  \frac{\left(N - k - 2\right) \left(N - k - 1\right)}{(N\!-\!2)(N\!-\!3)} \left(\frac{1}{N\!-\!2}\cdot v_{u_{11}}(s_1,s_2)\cdot 1_{(u_{11},u_{21})\in \mathcal{U}_F} + (1 - \frac{1}{N - 2}) [E_1 + E_2 + E_3 + E_4]\right) \right]
  \end{array} $}
\end{equation}

\begin{equation}
  \resizebox{.9\textwidth}{!}
  {%
$
  \setlength{\arraycolsep}{1pt}
  \begin{array}{llrl}
  A & = \left(1\!-\!\frac{1}{N\!-\!1}\right)  \left[ \frac{k\!-\!1}{N\!-\!2}\frac{k\!-\!2}{N\!-\!3} v_{u_{21}}(s_1,s_2) v_{u_{22}}(s_2,s_2) + 
   \frac{k\!-\!1}{N\!-\!2}\frac{N\!-\!k\!-\!1}{N\!-\!3} v_{u_{21}}(s_1,s_2) v_{u_{22}}(s_2,s_1) + \right. \\[0.5cm]
   & \left. \frac{N\!-\!k\!-\!1}{N\!-\!2}\frac{k\!-\!1}{N\!-\!3} v_{u_{21}}(s_1,s_1) v_{u_{22}}(s_2,s_2) + 
   \frac{N\!-\!k\!-\!1}{N\!-\!2}\frac{N\!-\!k\!-\!2}{N\!-\!3} v_{u_{21}}(s_1,s_1) v_{u_{22}}(s_2,s_1)\right] \\[0.5cm] 
   B_1 & = \frac{\left(k - 3\right) \left(k - 2\right)}{(N - 3) (N - 4)} v_{u_{21}}(s_1,s_2) v_{u_{22}}(s_2,s_2) \quad
   B_2 = \frac{\left(k - 2\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} v_{u_{21}}(s_1,s_1) v_{u_{22}}(s_2,s_2) \\[0.5cm] 
   B_3 & = \frac{\left(k - 2\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} v_{u_{21}}(s_1,s_2) v_{u_{22}}(s_2,s_1) \quad
   B_4 = \frac{\left(N - k - 2\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} v_{u_{21}}(s_1,s_1) v_{u_{22}}(s_2,s_1) \\[0.5cm]

   C_1 & = \frac{\left(k - 3\right) \left(k - 1\right)}{(N - 3) (N - 4)} v_{u_{21}}(s_1,s_2) v_{u_{22}}(s_2,s_2) \quad
   C_2 = \frac{\left(k - 1\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} v_{u_{21}}(s_1,s_1) v_{u_{22}}(s_2,s_2) \\[0.5cm] 
   C_3 & = \frac{\left(k - 2\right) \left(N - k - 2\right)}{(N - 3) (N - 4)} v_{u_{21}}(s_1,s_2) v_{u_{22}}(s_2,s_1) \quad
   C_4 = \frac{\left(N - k - 2\right)^{2}}{(N - 3) (N - 4)} v_{u_{21}}(s_1,s_1) v_{u_{22}}(s_2,s_1) \\[0.5cm]

   D_1 & = \frac{\left(k - 2\right)^{2}}{(N - 3) (N - 4)} v_{u_{21}}(s_1,s_2) v_{u_{22}}(s_2,s_2) \quad
   D_2 = \frac{\left(k - 2\right) \left(N - k - 2\right)}{(N - 3) (N - 4)} v_{u_{21}}(s_1,s_1) v_{u_{22}}(s_2,s_2) \\[0.5cm] 
   D_3 & = \frac{\left(k - 1\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} v_{u_{21}}(s_1,s_2) v_{u_{22}}(s_2,s_1) \quad
   D_4 = \frac{\left(N - k - 3\right) \left(N - k - 1\right)}{(N - 3) (N - 4)} v_{u_{21}}(s_1,s_1) v_{u_{22}}(s_2,s_1) \\[0.5cm]

   E_1 & = \frac{\left(k - 2\right) \left(k - 1\right)} v_{u_{21}}(s_1,s_2) v_{u_{22}}(s_2,s_2) \quad
   E_2 = \frac{\left(k - 1\right) \left(N - k - 2\right)}{(N - 3) (N - 4)} v_{u_{21}}(s_1,s_1) v_{u_{22}}(s_2,s_2) \\[0.5cm] 
   E_3 & = \frac{\left(k - 1\right) \left(N - k - 2\right)}{(N - 3) (N - 4)} v_{u_{21}}(s_1,s_2) v_{u_{22}}(s_2,s_1) \quad
   E_4 = \frac{\left(N - k - 3\right) \left(N - k - 2\right)}{(N - 3) (N - 4)} v_{u_{21}}(s_1,s_1) v_{u_{22}}(s_2,s_1) \\[0.5cm] 
  \end{array}$}
\end{equation}

The first term on the right side corresponds to the case that the learner and
the role model happened to be matched during the first stage,
followed by them being paired with another member of the population on the
second stage. The second terms corresponds to the case that the learner and the
role model interact with a mutant with a probability ($\frac{\left(k - 2\right)
\left(k - 1\right)}{(N\!-\!2)(N\!-\!3)}$). In the seconds stage, they can either
interact with each other $\frac{1}{N - 2}$ or not $(1 - \frac{1}{N - 2})$. If
they do not interact with each other, then each of the following can happen:
both of them interact with a mutant with a probability
$\frac{(k-3)(k-2)}{(N-4)(N-3)}$ and both interact with a resident with a
probability $\frac{(N-k-1)(N-k-2)}{(N-3)(N-4)}$. The last two possible pairs
are that either of them interacts with a resident whilst the other interacts
with a mutant, and this happens with a probability
$\frac{(N-k-2)(k-1)}{(N-4)(N-3)}$, and so on.

@@

In a similar fashion we can calculate the condition for which a population of
GTFT players can not be invaded by an ALLD mutant. Using the new formulation we
obtain the following probabilities \(x^{2}((u_{11}, u_{12}), (u_{21}, u_{22}))\) that the payoff of a randomly
chosen GTFT player is \((u_{11}, u_{12})\) and that the payoff of the ALLD player is \((u_{21}, u_{22})\),
